\chapter{Board of Directors}

\section{General Powers}

All of the business and affairs of the Corporation shall be managed and
controlled by the Board of Directors.  The following are the matters which must
be submitted to, and receive the approval of, the Board of Directors:

\begin{enumerate}

    \item Annual financial statements.

    \item The amendment or restatement of these bylaws or the articles of
        organization.

    \item The merger, consolidation, or dissolution of the corporation.

    \item The sale, lease, exchange, pledge, or mortgage of any substantial
        part of the assets of the Corporation, or any contract, option,
        or other agreement with respect thereto.

    \item Such other matters as to which the Board of Directors determines by
    resolution that such submission is advisable.

\end{enumerate}

\section{Number, Election, and Tenure}

At the regular annual meeting, the existing Directors shall elect Directors for
terms commencing on the first day of the next August and continuing for three
years and until their respective successors are elected and take office. Persons
who are Directors by virtue of election are referred to as `elected Directors'
in these Bylaws. The number of elected Directors shall not be less than four or
more than ten. In addition, unless already Directors by virtue of election, the
President, the Treasurer, and the House Manager of the Eta Tau Chapter of Beta
Theta Pi shall be ex officio Directors of the Corporation during the times such
persons occupy their offices as President, Treasurer, and House Manager,
respectively, of the Eta Tau Chapter of Beta Theta Pi. These three Directors are
referred to as `ex officio Directors' in these Bylaws.

In order to be elected and in order to hold office, each elected Director must
be a person who was conferred a Bachelor's Degree or Master's Degree by
Worcester Polytechnic Institute, and at the time so conferred was either an
initiated Brother in good standing of or a Sweetheart in good standing of the
Eta Tau Chapter of Beta Theta Pi.

In the event that the number of elected Directors falls to less than four,
through resignations or any other cause, the Board of Directors shall take no
action other than the election of Directors until the number of elected
Directors is at least four.

\section{Staggered Terms}

The elected Directors shall be divided into three groups about equal in number
with the Directors comprising each group having terms of office that expire in a
different year than of Directors in the other groups, so that the terms of
office of about one-third of elected Directors expire each year.

\section{Regular Meetings}

A regular annual meeting of the Board of Directors shall be held in August of
each year, at such time and place as shall be designated by the President or
Vice President in the notice of the meeting for the purpose of electing
Directors and officers and for the transaction of such other business as may
come before the meeting.  The Board of Directors may provide by resolution for
the holding of additional regular meetings.

The Directors, all officers of the Corporation, and all persons who are alumni
in good standing of the Eta Tau Chapter of Beta Theta Pi shall be
permitted to attend any regular meeting of the Board of Directors.  Other
persons may be, but need not be, excluded.

\section{Special Meetings}

Special meetings of the Board of Directors may be called by order of the
Chairman of the Board of Directors or the President, and shall be held at such
time and place as shall be designated by the Chairman or President in the notice
of the meeting.

The Directors and all officers of the Corporation shall be permitted to attend
any special meeting of the Board of Directors.  Other persons may be, but need
not be, excluded.

\section{Electronic Participation in Meetings}

The Board of Directors may permit any or all Directors to participate in a
regular or special meeting by, or conduct the meeting through the use of, any
electronic means of communication by which all Directors participating may
simultaneously hear each other during the meeting. A Director participating in a
meeting by this means is considered to be present in person at the meeting, and
is said to be `participating electronically'.


\section{Notice of Meetings}

Notice of the time and place of any meeting of the Board of Directors shall be
delivered personally, by mail, or by email, to each of the elected Directors;
and shall be delivered to the ex officio Directors personally, by mail, by
email, or by mail or email to the Eta Tau Chapter of Beta Theta Pi at such
mailing address or email address as the Eta Tau Chapter of Beta Theta Pi shall
designate for receiving such notice, which shall constitute notice to all of the
ex officio Directors. Notice shall be delivered at least
seven days prior if the Directors are permitted to participate electronically,
and at least fourteen days prior if any Director is not permitted to participate
electronically. A Director may waive notice. The attendance of a Director at a
meeting shall constitute a waiver of notice of that meeting, except where a
Director attends a meeting for the purpose of objecting to the transaction of
business because the meeting is not lawfully called or convened. Neither the
business to be transacted at, nor the purpose of, any regular or special meeting
of the Board of Directors need be specified in the notice of the meeting unless
required by statute.

\section{Quorum}

Four Directors present in person shall constitute a quorum for the transaction
of business at any meeting of the Board of Directors, unless the number of
Directors is less than four, in which case the quorum shall be three, and unless
the presence of a greater number is required by law, in which case the quorum
shall be such number as the law requires.

\section{Manner of Acting}

\subsection{Formal Action by Directors}

The act of a majority of Directors present at a meeting at which a quorum is
present shall be the act of the Board of Directors.

\subsection{Informal Action by Directors}

No action of the Board of Directors shall be valid unless taken at a meeting at
which a quorum is present, excepting any action taken without a meeting for
which a consent in writing, setting forth the action so taken, is signed by each
Director entitled to vote.

\section{Resignations and Removal}

Any elected Director may resign from the Board of Directors at any time by
giving notice in writing to the President or Secretary of the Corporation, and
unless otherwise specified therein, the acceptance of such resignation shall not
be necessary to make it effective.

Any elected Director who is absent from all meetings of the Board of Directors
for a thirteen month period entirely within his term of office, the number of
meetings in the period for which notice was properly given being at least two,
may be removed by the Board of Directors for cause of job abandonment.

\section{Vacancies}

Any vacancy occurring in an elected Directorship may be filled by the Board of
Directors for the unexpired portion of the term of office.  Any Directorship to
be filled by reason of an increase in the number of Directors shall be filled by
the Board of Directors.

\section{Compensation}

Directors shall not receive any stated salaries for their services but, by
resolution of the Board of Directors, expenses of attendance may be allowed for
attendance at each regular or special meeting of the Board of Directors.

\section{Procedure}

The Chairman of the Board of Directors, or in his absence, the President, shall
preside at meetings of the Board of Directors. The Board of Directors may adopt
its own rules of procedure which shall not be inconsistent with these Bylaws.

