\chapter{Miscellaneous}

\section{Books and Records}

The Corporation shall keep correct and complete books and records of account
and the minutes of the proceedings of the Board of Directors.

\section{Document Retention}

The Corporation shall keep documents and records according to this schedule:

\begin{itemize}

    \item Articles of Organization: Keep in perpetuity. 

    \item Bylaws: Keep current and past versions in perpetuity.  

    \item Tax filings: Keep in perpetuity.

    \item Financial records: Destroy after 7 years. 

    \item Payroll and employment records: Keep in perpetuity. 

    \item Meeting minutes and records: Keep in perpetuity. 

    \item Contracts: Destroy after 7 years after end date of contract. 

    \item Documents related to any legal issues or lawsuits: Keep in perpetuity. 

    \item IRS Form 990: Keep in perpetuity.

    \item Other types of documents: Will be retained for a period of time to be
        determined by the Board of Directors.

\end{itemize}

\section{Fiscal Year}

The fiscal year of the Corporation shall begin on the first day of July of each
calendar year and shall end on the last day of June.

\section{Seal}

The Board of Directors shall provide a corporate seal.

\section{Loans to Officers and Directors Prohibited}

No loans shall be made by the Corporation to its officers or Directors. The
Directors of the Corporation who vote for or assent to the making of a loan to
an officer or Director of the Corporation, and any officer or officers
participating in the making of such loan, shall be jointly and severally liable
to the Corporation for the amount of such loan until the repayment thereof.

\section{Additional Organizations}

The Board of Directors may authorize the formation of such auxiliary
organizations as would in the judgment of the Board assist in the fulfillment
of the purposes of the Corporation.

\section{Rules}

The Board of Directors may adopt, amend, or repeal rules not inconsistent with
these Bylaws for the management of the internal affairs of the Corporation and
the governance of its officers, agents, and committees.

\section{Conflicts of Interest}

No contract or transaction between this Corporation and one or more of its
Directors or officers, or between this Corporation and any other corporation,
partnership, association, or other organization in which one or more of its
directors or officers are Directors or officers of this Corporation or in which
one or more of the Directors or officers of this Corporation have a financial
interest, shall be void or voidable solely for this reason, or solely because
such Director is present at or participates in the meeting of the Board of
Directors or committee thereof which authorizes the contract or transaction, or
solely because his or their votes are counted for such purpose, if the material
facts as to his or their relationship or interest and as to the contract or
transaction are disclosed or are known to the Board of Directors or the
committee, and the Board of Directors or the committee in good faith authorizes
the contract or transaction by the affirmative votes of a majority of the
disinterested Directors even though the disinterested Directors be less than a
quorum; or the contract or transaction is fair as to the Corporation as of the
time it is authorized, approved, or ratified by the Board of Directors or a
committee thereof.

\section{Amendment of Bylaws}

These bylaws may be amended by a majority of the Directors.\footnote{Note that
``a majority of the Directors'' is not the same as ``a majority of Directors
present at a meeting at which a quorum is present''.}
