\chapter{Officers}

\section{Officers}

The officers of the Corporation shall be a President, a Vice President, a
Secretary, and a Treasurer. The Corporation may, at the direction of the Board
of Directors, have additional officers including, without limitation, other
vice presidents, one or more assistant secretaries, and one or more assistant
treasurers. One person may hold two or more offices except the person holding
the office of President may not hold another office.

\section{Election and Term of Office}

The officers of the Corporation shall be elected annually by the Board of
Directors at its annual meeting. If the election of officers is not held at
such meeting, it shall be held as soon thereafter as possible. Offices may be
filled or new offices created and filled at any meeting of the Board of
Directors. Each elected officer shall hold office for a term of two years and
until his successor is elected unless he sooner resigns or is removed.

\section{Resignations and Removal}

Any officer may resign his office at any time by giving notice in writing to
the President or Secretary of the Corporation, and unless otherwise specified
therein, the acceptance of such resignation shall not be necessary to make it
effective.

Any officer elected by the Board of Directors may be removed by the Board of
Directors whenever in their judgment the interests of the Corporation would be
furthered thereby.

\section{Vacancies}

A vacancy in any office may be filled by the Board of Directors for the
unexpired portion of the term of office.

\section{President}

The President shall be the chief executive officer of the Corporation and have
general supervision of all of the business and affairs of the Corporation. The
President's responsibilities shall include, without limitation, the following:

\begin{enumerate}

    \item The day-to-day administration of the Corporation.

    \item Acting as the representative of the Corporation to the public, as
        well as to governmental and voluntary organizations.

    \item Making policy proposals to the Board of Directors.

    \item Long-term planning.

    \item Assigning overall responsibility for corporate management.

    \item Reporting to the Board of Directors on the performance of corporate
        functions.

\end{enumerate}

In general, the President shall perform all duties incident to the function of
chief executive officer and such other duties as may be prescribed by the Board
of Directors from time to time.

\section{Vice President}

One or more vice presidents may be elected from among the elected Directors
and, in the absence of the President, the Vice President first, and second any
other elected vice presidents, in order of their election, shall perform the
duties of the President. The Vice President and other vice presidents shall
perform such other duties as may be prescribed by the Board of Directors from
time to time.

\section{Treasurer}

The Treasurer shall, subject to the direction of the President, have charge and
custody of and be responsible for all funds and securities of the Corporation
from any source whatsoever; deposit all such monies in the name of the
Corporation in such banks, trust companies, or other depositories as the Board
of Directors may select; and perform such other duties as may from time to time
be assigned to him by the President or prescribed by the Board of Directors.

If required by the Board of Directors, the Treasurer shall give a bond for the
faithful discharge of his duties in such sum and with such surety as the Board
of Directors shall determine.

\section{Secretary}

The Secretary shall, subject to the direction of the President, keep the
minutes of the meetings of the Board of Directors; assure that minutes of all
meetings of other committees are prepared and filed with the records of the
Corporation; assure that all notices are given in accordance with the
provisions of these Bylaws or as required by law; be custodian of the corporate
records and of the seal of the Corporation; assure that the seal of the
Corporation is affixed to all documents, the execution of which on behalf of
the Corporation under its seal is authorized in accordance with the provisions
of these Bylaws; and perform such other duties as may from time to time be
assigned to him by the President or prescribed by the Board of Directors.

\section{Assistant Treasurers and Assistant Secretaries}

The assistant treasurers shall perform such duties as may from time to time be
assigned to them by the Treasurer or prescribed by the Board of Directors.

The assistant secretaries shall perform such duties as may from time to time be
assigned to them by the Secretary or prescribed by the Board of Directors.

\section{Compensation}

The compensation of the officers, if any, shall be fixed by resolutions of the
Board of Directors but no such resolution will create any contractual right to
the continuation of such compensation for any period of time.

